---
title: "Investigation Genomic Content vs Expression of Contigs Across KOs"
date: April 29, 2015
author: Wesley GOI
runtime: shiny
output: html_document
---

```{r lib, echo=FALSE, message=FALSE, warning=FALSE}
library(magrittr)
library(knitr)
library(ggplot2)
library(shiny)
library(dplyr)
library(ggvis)
theme_set(theme_bw())
```

```{r settings, echo=FALSE}
opts_chunk$set(echo=FALSE)
```

```{r readData, eval=FALSE}
#reads in data
cDNA = read.csv("out/map.0102/cDNA_kocontigs.csv") %>% select(contigID:ko)
gDNA = read.csv("out/map.0102/gDNA_kocontigs.csv") %>% select(contigID:ko)
```


## Implementating RPKM

$RPKM = \frac{10^{9} \times C }{n \times L}$

| Variable | Description                                                            |
| ---      | ----                                                                   |
| C        | number of reads mappable to the Max Diversity (MD) Region (Using Blat) |
| N        | Total number of reads mappable to MD regions                           |
| L        | Length of the MD Region                                                |


```{r rpkm-func, echo=TRUE}
#Fxn for calculating RPKM based on the above
rpkm       =  function(count, allcount, length) {
    #change to numeric (bit size too small for integers)
    count     %<>%  as.numeric
    allcount  %<>%  as.numeric
    length    %<>%  as.numeric
    (10^9 * count) / (allcount* length)
}
```

```{r addRpkm, eval=FALSE}
#Introduce new RPKM columns
cDNA$rpkm   =   with(cDNA, rpkm(Freq, sum(Freq), length))   #na.omit %>% log10 %>% txtdensity
gDNA$rpkm    =   with(gDNA, rpkm(Freq, sum(Freq), length))  #na.omit %>% log10 %>% txtdensity
```

## 1. All Contigs, All KOs

```{r allKO, eval=FALSE}
#All in one
allKODF = merge(
      by = c("ko","contigName", "ko"),
      cDNA %>% select(-type, -length, -contigID),
      gDNA %>% select(-type, -length, -contigID),
      suffixes = c("_cDNA", "_gDNA"),
      all=T
)
allKODF[is.na(allKODF)] = 0
save(allKODF, "out/nxx.0101.in.rda")
```

```{r loadRDA}
load("nxx.0101.in.rda")
```

```{r}
kotable %<>% mutate(fullName = paste(ko, koname.ko..ko.definition, sep=" - ")) %>% select(ko, fullName)
```

```{r plot1, warning=FALSE, eval=TRUE}
qplot(rpkm_cDNA, rpkm_gDNA, geom=c("point"), data=allKODF, alpha=0.2)     +
scale_x_log10()                                                           +
scale_y_log10()                                                           +
ggtitle("Comparison of read abundances (rpkm) of All Contigs in All KOs")+ 
theme(legend.position="none")
```

#### Log10 Distribution of normalised (rpkm) mappable cDNA reads (Expression) to all KO Contigs
```{r plot2, warning=FALSE}
allKODF %>% ggvis(~log10(rpkm_cDNA)) %>%  layer_densities() %>% set_options(width=150, height=100)
```

#### Log10 Distribution of normalised (rpkm) mappable gDNA reads (Genomic) to all KO Contigs
```{r plot3, warning=FALSE}
allKODF %>% ggvis(~log10(rpkm_gDNA)) %>%  layer_densities() %>% set_options(width=150, height=100)
#qplot(log10(rpkm_gDNA), data=allKODF, geom="density")+ ggtitle("gDNA")
```

## 2. Partitioned by KO

```{r app}
shinyApp(
ui = bootstrapPage(
               selectInput("ko", "Choose a ko:", choices = kotable$fullName, selected = allKODF$ko[1], width="100%"),
               checkboxInput("toLog", "log10", value = TRUE),
 tags$table(
    tags$td(ggvisOutput("Everything")),
    tags$td(ggvisOutput("react1"))
  )
               ),
server = function(input, output){

    chosenKO = reactive({
        koID = substr(start=1, stop=6, x=input$ko)
    allKODF %<>% filter(ko==koID)
    if(input$toLog){
        allKODF$rpkm_cDNA %<>% log10    #taking log creates -Inf
        allKODF$rpkm_gDNA %<>% log10
        allKODF
    }else{
        allKODF
    }
  })

koDF = reactive({
    if(input$toLog){
        chosenKO() %>% filter(rpkm_cDNA != -Inf, rpkm_gDNA != -Inf)
    }else{
        chosenKO()
    }
})

thedf = reactive({
    if(input$toLog){
            chosenKO() %>% mutate(isExpressed=ifelse(rpkm_cDNA ==- Inf,"no","yes")) #%>%
    }else{
            chosenKO() %>% mutate(isExpressed=ifelse(rpkm_cDNA == 0,"no","yes")) #%>%
    }
})

theTitle = reactive({
ifelse(input$toLog,
"gDNA Rpkm distribution (contigs without observable expression)",
"gDNA Rpkm distribution")
})

#renderPlot({qplot(rpkm_cDNA, rpkm_gDNA, data=koDF()) })
    koDF %>% ggvis(~rpkm_cDNA, ~rpkm_gDNA) %>% layer_points() %>% 
    set_options(width=350, height=300) %>%
    bind_shiny("Everything")

    thedf %>% ggvis(~rpkm_gDNA, fill=~isExpressed) %>%
    group_by(isExpressed) %>%
    layer_histograms() %>%
    set_options(width=350, height=300) %>%
    bind_shiny("react1")
}
#options = list(height = 500)
)

```

```{r sessionInfo}
sessionInfo()
```
